Algorithmically Trading like a Human with GPT-J

### 2021-10-05 paper.tex
Made change
Started background added sources
moar background shit

\documentclass[conference]{IEEEtran}
\hyphenation{op-tical net-works semi-conduc-tor}
\usepackage{svg}
\usepackage{float}
\usepackage{tikz}
\usepackage{makecell}
\usepackage{hyperref}
\begin{document}

@@

\section{Background \& Related Works}
\section{Execution Plan}
\subsection{Requirements \& Goals}
\subsubsection{Functional requirements (user stories)}
\begin{itemize}
\item As a finance researcher, I want to quantify the ability of news releases, SEC filings, and social media posts to move stock prices.
\item As an AI researcher, I want to evaluate the viability of using GPT-J as a stock movement indicator so that I can understand the power of GPT-J to understand complex real-world interactions.
\item As an algorithmic trader, I want to evaluate the viability of using GPT-J as a stock movement indicator so that I can make more-informed trading decisions.
\end{itemize}
\subsubsection{Non-functional requirements}
\begin{enumerate}
    \item[•] I will evaluate the correlations between the following items:
    \begin{enumerate}
        \item The release of SEC filings for company X and large movements in the stock price of company X.
        \item The release of news stories mentioning company X and large movements in the stock price of company X.
        \item The posting of tweets or other social media posts mentioning company X and large movements in the stock price of company X.
    \end{enumerate}
    \item[•] I evaluate the best ways of formatting prompts for GPT-J to increase output accuracy and consistency across varying inputs. Some options might include:
    \begin{enumerate}
        \item Providing a form for GPT-J to fill out appended to the end of the input data.
        \item Asking GPT-J a direct question appended to the end of the input data.
        \item Appending a universe current stock prices to the beginning of the input.
        \item Appending multiple news stories from the past days and weeks at the beginning of the input.
    \end{enumerate}
    \item[•] I will deploy the best model from my previous evaluations and test it on live stock market data. I will compare the model's performance against market indices like the S\&P 500. 
\end{enumerate}

\begin{figure}[H]
    \centering
    \scalebox{0.8}{
    \definecolor{lblue}{RGB}{220, 234, 240}
    \definecolor{dblue}{RGB}{0, 21, 79}
    \newcommand\bluebox[3]{\filldraw [draw=dblue,fill=lblue, line width=0.4mm] (#1-1.75,#2-0.75) rectangle (#1+1.75,#2+0.75) node[text=dblue, font=\footnotesize][midway] {\makecell[l]{#3}}}
    \newcommand\bluearrow[4]{\draw[dblue, -latex, line width=0.8mm] (#1,#2-0.75) -- (#3,#4+0.75);}
    \newcommand\bluearrownooffset[4]{\draw[dblue, -latex, line width=0.8mm] (#1,#2) -- (#3,#4);}
    \newcommand\blueline[4]{\draw[dblue, line width=0.8mm] (#1,#2) -- (#3,#4);}
    \begin{tikzpicture}
        \bluebox{0}{0}{\textbf{Gather test dataset.}\\(SEC filings, news, social\\media, stock price data)};
        \bluebox{0}{-2}{\textbf{Evaluate correlations}\\\textbf{between media release}\\\textbf{\& price movement.}};
        \bluebox{2}{-4}{\textbf{Change type of}\\\textbf{input media.}};
        \bluebox{0}{-6}{\textbf{Fine-tune training}\\\textbf{on GPT-J.}};
        \bluebox{2}{-8}{\textbf{Change format of}\\\textbf{input prompt.}};
        \bluebox{0}{-10}{\textbf{Evaluate prediction}\\\textbf{accuracy.}};
        \bluebox{0}{-12}{\textbf{Test and evaluate}\\\textbf{on live data.}};
        \bluearrow{0}{0}{0}{-2};
        \bluearrow{-1}{-2}{-1}{-6};
        \blueline{0.25}{-4}{-1}{-4};
        \bluearrow{-1}{-6}{-1}{-10};
        \blueline{0.25}{-8}{-1}{-8};
        \bluearrow{0}{-10}{0}{-12};
        \blueline{1.75}{-10}{4.21}{-10};
        \bluearrownooffset{2.75}{-10}{2.75}{-8.75};
        \blueline{4.25}{-4.04}{4.25}{-10.04};
        \bluearrownooffset{4.29}{-4}{3.75}{-4};
        \blueline{2.75}{-7.25}{2.75}{-5.96};
        \bluearrownooffset{2.75}{-6}{1.75}{-6};
    \end{tikzpicture}
    }
\caption{Execution Flow}
\end{figure}

\section{Conclusion}
The conclusion goes here.

>>>>

\documentclass[conference]{IEEEtran}
\hyphenation{op-tical net-works semi-conduc-tor}
\usepackage{svg}
\usepackage{float}
\usepackage{tikz}
\usepackage{makecell}
\usepackage{url}
\def\UrlBreaks{\do\/\do-}
\usepackage{breakurl}
\usepackage[breaklinks]{hyperref}
\begin{document}

@@

\section{Background \& Related Works}
Many neural network structures and methods have been used to create trading algorithms. Some types include: 
\begin{itemize}
    \item Recurrent neural networks (RNNs) \& Long short-term memory (LSTMs) \cite{Chen2017}\cite{Mehta2021}.
    \\\emph{These are the most widely used network architectures for trading \cite{Gu2020}. An LSTM trained on 900,000 sequences of length 30 days of Chinese stock market data yeilded an improvement of 12.9\% in prediction accuracy over a random guess \cite{Chen2015}.}
    \item Convolutional Neural Networks (CNNs) \cite{Gu2020}
    \\\emph{CNNs can be used by converting time-series data into images \cite{Sezer2018}. Or they can be used to extract sentiment features from text \cite{Shi2020}.}
    \item Deep reinforment learning (DRN).
    \begin{itemize}
        \item Deep Q-learning \cite{Wang2017} \cite{Nan2020}.
        \item Deep robust reinforcement learning \cite{Li2019}.
    \end{itemize}
    \item Conventional deep learning \cite{Day2016}.
    \item Transformer networks \cite{Schmitz2020}.
\end{itemize}
Most relevent to our work are methods that incorperate sentiment analysis of news sources. Mehta et al. (2021) evaluated a sentiment analysis methods and found that LSTMs could properly classify news tweets as indicative of positive or negative price movement with an accuracy of 92\% correct \cite{Mehta2021}. Nan \& Zaiane (2020) found that adding sentiment analysis to a Deep-Q learning algorithm could improve the sharpe ratio of the agent by a factor greater than 2 in their test cases. \cite{Nan2020}.

\section{Execution Plan}
\subsection{Requirements \& Goals}
\subsubsection{Functional requirements (user stories)}
\begin{itemize}
\item As a finance researcher, I want to quantify the ability of news releases, SEC filings, and social media posts to move stock prices.
\item As an AI researcher, I want to evaluate the viability of using GPT-J as a stock movement indicator so that I can understand the power of GPT-J to understand complex real-world interactions.
\item As an algorithmic trader, I want to evaluate the viability of using GPT-J as a stock movement indicator so that I can make more-informed trading decisions.
\end{itemize}
\subsubsection{Non-functional requirements}
\begin{enumerate}
    \item[•] I will evaluate the correlations between the following items:
    \begin{enumerate}
        \item The release of SEC filings for company X and large movements in the stock price of company X.
        \item The release of news stories mentioning company X and large movements in the stock price of company X.
        \item The posting of tweets or other social media posts mentioning company X and large movements in the stock price of company X.
    \end{enumerate}
    \item[•] I evaluate the best ways of formatting prompts for GPT-J to increase output accuracy and consistency across varying inputs. Some options might include:
    \begin{enumerate}
        \item Providing a form for GPT-J to fill out appended to the end of the input data.
        \item Asking GPT-J a direct question appended to the end of the input data.
        \item Appending a universe current stock prices to the beginning of the input.
        \item Appending multiple news stories from the past days and weeks at the beginning of the input.
    \end{enumerate}
    \item[•] I will deploy the best model from my previous evaluations and test it on live stock market data. I will compare the model's performance against market indices like the S\&P 500. 
\end{enumerate}

\begin{figure}[H]
    \centering
    \scalebox{0.8}{
    \definecolor{lblue}{RGB}{220, 234, 240}
    \definecolor{dblue}{RGB}{0, 21, 79}
    \newcommand\bluebox[3]{\filldraw [draw=dblue,fill=lblue, line width=0.4mm] (#1-1.75,#2-0.75) rectangle (#1+1.75,#2+0.75) node[text=dblue, font=\footnotesize][midway] {\makecell[l]{#3}}}
    \newcommand\bluearrow[4]{\draw[dblue, -latex, line width=0.8mm] (#1,#2-0.75) -- (#3,#4+0.75);}
    \newcommand\bluearrownooffset[4]{\draw[dblue, -latex, line width=0.8mm] (#1,#2) -- (#3,#4);}
    \newcommand\blueline[4]{\draw[dblue, line width=0.8mm] (#1,#2) -- (#3,#4);}
    \begin{tikzpicture}
        \bluebox{0}{0}{\textbf{Gather test dataset.}\\(SEC filings, news, social\\media, stock price data)};
        \bluebox{0}{-2}{\textbf{Evaluate correlations}\\\textbf{between media release}\\\textbf{\& price movement.}};
        \bluebox{2}{-4}{\textbf{Change type of}\\\textbf{input media.}};
        \bluebox{0}{-6}{\textbf{Fine-tune training}\\\textbf{on GPT-J.}};
        \bluebox{2}{-8}{\textbf{Change format of}\\\textbf{input prompt.}};
        \bluebox{0}{-10}{\textbf{Evaluate prediction}\\\textbf{accuracy.}};
        \bluebox{0}{-12}{\textbf{Test and evaluate}\\\textbf{on live data.}};
        \bluearrow{0}{0}{0}{-2};
        \bluearrow{-1}{-2}{-1}{-6};
        \blueline{0.25}{-4}{-1}{-4};
        \bluearrow{-1}{-6}{-1}{-10};
        \blueline{0.25}{-8}{-1}{-8};
        \bluearrow{0}{-10}{0}{-12};
        \blueline{1.75}{-10}{4.21}{-10};
        \bluearrownooffset{2.75}{-10}{2.75}{-8.75};
        \blueline{4.25}{-4.04}{4.25}{-10.04};
        \bluearrownooffset{4.29}{-4}{3.75}{-4};
        \blueline{2.75}{-7.25}{2.75}{-5.96};
        \bluearrownooffset{2.75}{-6}{1.75}{-6};
    \end{tikzpicture}
    }
\caption{Execution Flow}
\end{figure}
\section{Implementation}
\section{Conclusion}
The conclusion goes here.
